DATA 621 - Business Analytics and Data Mining

### 2020-11-22 HW5/HW5-Draft.Rmd
cleanup

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(corrplot)
library(data.table)

@@

### Negative Binomial Model # 1
```{r m1NBTrain, cache=TRUE}
glmc <- glm.control(maxit = 25, epsilon = 1e-12)
set.seed(72)
m1NBFit2a <- glm.nb(TARGET ~ . + FreeSulfurDioxide:TotalSulfurDioxide +
                      AcidIndex * FixedAcidity * VolatileAcidity * pH +
                      Rated:STARS + LabelAppeal:Rated +
                      LabelAppeal:Rated:STARS - INDEX - STARS,
                    data = m1trnXimp, control = glmc, link = log,
                    na.action = na.exclude)

m1NBFit2b <- stepAIC(m1NBFit2a, direction = 'both', trace = 1)

# Save AIC
m1NBFitAIC <- AIC(m1NBFit2b)
```

\small
```{r m1NBTable}
# Print results. This needed to ne in its own section so that the LaTeX commands
# to change the text size can be wrapped around it.
kable(summary(m1NBFit2b)$coefficients,
      caption = "Model 1 Negative Binomial Regression Output")
```
\normalsize

>>>>

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(knitr)
library(MASS)
library(caret)
library(corrplot)
library(data.table)

@@

### Negative Binomial Model # 1
As the dispersion from the Poisson model was less than 1, at first blush, it is
not expected that the negative binomial model will outperform the Poisson.

```{r m1NBTrain, cache=TRUE}
glmc <- glm.control(maxit = 25, epsilon = 1e-14)
set.seed(72)
m1NBFitStart <- glm.nb(TARGET ~ . + FreeSulfurDioxide:TotalSulfurDioxide +
                         AcidIndex * FixedAcidity * VolatileAcidity * pH +
                         Rated:STARS + LabelAppeal:Rated +
                         LabelAppeal:Rated:STARS - INDEX - STARS,
                       data = m1trnXimp, control = glmc, link = log)

m1NBFit <- stepAIC(m1NBFitStart, direction = 'both', trace = 0)

# Save AIC
m1NBFitAIC <- AIC(m1NBFit)
```

\small
```{r m1NBTable}
# Print results. This needed to ne in its own section so that the LaTeX commands
# to change the text size can be wrapped around it.
kable(summary(m1NBFit)$coefficients,
      caption = "Model 1 Negative Binomial Regression Output")
```
\normalsize

```
                                       Df   AIC
<none>                                    31905
- Sulphates                             1 31906
+ pH:AcidIndex                          1 31906
- FreeSulfurDioxide:TotalSulfurDioxide  1 31906
- VolatileAcidity:AcidIndex             1 31906
+ Density                               1 31906
+ ResidualSugar                         1 31906
+ VolatileAcidity:pH                    1 31907
+ CitricAcid                            1 31907
+ FixedAcidity:pH                       1 31907
+ FixedAcidity:VolatileAcidity          1 31907
- FixedAcidity:AcidIndex                1 31907
- pH                                    1 31907
- Alcohol                               1 31907
- Chlorides                             1 31907
- LabelAppeal:Rated:STARS               1 31917
```
